---
title: "Reannan_McDaniel_HW3"
author: "Reannan McDaniel"
date: "6/28/2019"
output: 
  html_document:
    keep_md: yes
---

```{r}
library(RCurl)
library(plyr)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(car)
library(naniar)
library(viridis)
library(scales)
```


# 2a.
## Read in titanic.csv file
## Assign to df
```{r}

URL <- getURL("https://raw.githubusercontent.com/rmcdaniel-smu/MSDS-SMU/master/titanic.csv")
Titanic_df <- read.csv(text = URL)
str(Titanic_df)
length(Titanic_df$Sex)
```

# 2b.
## Count of females and males on the Titanic
# Females = 314
# Males = 577
```{r}

str(Titanic_df)
summary(Titanic_df)
Gender <- as.numeric(Titanic_df$Sex)
hist(Gender)
```

# 2c. 
## # 2c.
## Find the mean of Age, Fare and Survived
# Mean Age = NA
# Mean Fare = 32.20
# Mean Survived = 0.383
```{r}
mean(Titanic_df$Age)
mean(Titanic_df$Fare)
mean(Titanic_df$Survived)
```

# 3a.
## Create objects for median Age, min and max Duration of Sleep, and the mean and standard deviation of the Rosenberg Self Esteem Scale
```{r}
URL2 <- getURL("http://talklab.psy.gla.ac.uk/L1_labs/lab_1/homework/sleep_data_01.csv")
Sleep1 <- read.csv(text = URL2)
str(Sleep1)
summary(Sleep1)
MedAge <- median(Sleep1$Age)
MinDuration <- pmin(Sleep1$Duration)
MaxDuration <- pmax(Sleep1$Duration)
MeanRSES <- mean(Sleep1$RSES)
SdRSES <- sd(Sleep1$RSES)
```

# 3b.
## Create data frame from 3a.
```{r}
Records <- data.frame(MedAge, MinDuration, MaxDuration, MeanRSES, SdRSES)
```

#3c.
## Change the column names to MedianAge, SelfEsteem, SE_SD and DurationRange
```{r}

MedianAge <- median(Sleep1$Age)
MinDuration <- pmin(Sleep1$Duration)
MaxDuration <- pmax(Sleep1$Duration)
SelfEsteem <- mean(Sleep1$RSES)
SE_SD <- sd(Sleep1$RSES)
Records1 <- data.frame(MedianAge, MinDuration, MaxDuration, SelfEsteem, SE_SD)
```

#4a. 