---
title: "Reannan_McDaniel HW2"
author: '"Reannan"'
date: "5/20/2019"
output: html_document
---

```{r, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

# What is a basic workflow for repoducible research?  
## Be able to right a code that any researcher can reproduce and provide an analysis.  

# What are five practical tips for making research reproducible?  
## Save    
## Not complex    
## Easily readable   
## Order    
## Share    .  

# Give an example of you might implement each tip.    
# **Save**  
## Ensure all steps and notes are included in file. Use a text editor to save.   
# **Not complex**
## Don't write a code that no one can understand. Keep it simple. 
# **Easily readable**  
## Code is easy to follow and understand  
# **Order**  
## Steps and processes make sense.
# **Share**  
## Share with other researchers in github or other web sources.  

# Which one of these do you think will be the most difficult?  
## **Not Complex**  I tend to make things harder than they need to be.  

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=TRUE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
